Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-06 paper/main.tex
better explain AO and AV categories and regressors

% AO annotation
For the analysis of the AO data, we extended a publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% reference to table with rules and examples
A complete overview of all 18 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
disco'', ``the platoon wades through a rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``Jenny as a
teenager'').

@@

\todo[inline]{Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
    ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum
    GLM unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter;
    COH: I dropped the table of counts per segment.  The information is
    redundant since the counts are not the count of events of the actual
regressors (cf. Table \ref{tab:av-events})}

@@

\paragraph{audio-description: regressors}
% first level analysis regressors AO: events
For the analysis of the AO stimulus, we created regressors correlating with the
occurrence of descriptive nouns spoken by the narrator that were added to the
original annotation of speech \citep{haeusler2020speechanno}.
% AV events
For the AV stimulus, we created regressors correlating with movie cuts provided
by another previously published annotation \citep{haeusler2016cutanno}.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}

% procedure
Both annotations were split into eight parts corresponding to the eight stimulus
segments.
% AO events
To create regressors for the AO analysis, we used all of the original 19
categories of descriptive nouns except ``\texttt{++}'' (i.e. cues regarding
time).
% pooling
Some categories that were similar but offered only a small amount of counts were
pooled resulting in eleven new categories that served as experimental conditions
(see Table \ref{tab:ao-events}).
% setting beats other category
Events that fell into one of the two setting-related categories
(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
treated as belonging to the setting-related category (e.g. ``Jenny as a
teenager'').
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.

\todo[inline]{Gab es ein separates null-event für jeden zeitraum zwischen zwei
annotierten events oder war das ein regressor der immer wieder kam?}
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that category in that segment.\todo{wenn ich "null regressor" nehme, darf
ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen?
Hatte, glaube ich, Jeanette Mumford in einem ihren Videos mal gesagt}

\todo[inline]{Das mit den "five additional categories" habe ich nicht
verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
durchdrungen, und ich glaube damit werde ich nicht alleine sein.}
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after a cut, and to create contrasts of cross-modal negative
control (see details below).
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms" ?!?}
%
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories, the
five movie cut-related categories, and the two low-level confounds can be found
in Table \ref{tab:ao-events}.

% modeling of regressors from events
Events of both stimuli were convolved with a double gamma hemodynamic response
function (HRF).

@@

\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
zwischen zwei Gesichtern sein?!?; COH: that should be clearer now as the
explanation of the regressors immediately follows the description of the
annotation}

\todo[inline]{besser erklären (was heißt "unfamilar perspective"? Ab wann ist
ein setting "familiar"?)}

@@

@@

% AV regressors/events
To create regressors for the AV analysis, we categorized the depicted location
in the frame following one of the 869 cuts into five categories (see Table
\ref{tab:av-events}): 1) a cut into an unfamiliar setting (\texttt{vse\_new}),
2) a cut into a familiar setting (\texttt{vse\_old}), 3) a switch of room/locale
within a setting (\texttt{vlo\_ch}), 4) a cut to an unfamiliar perspective
(\texttt{vpe\_new}), and 5) a cut to a familiar perspective (\texttt{vpe\_old}).
% null regressor
Here again, a null regressor was chosen for segment if it did not contain an
event of specific category.
% no cut condition: intro
A sixth regressors (\texttt{no\_cut}) serving a control condition and to create
negative control contrasts. Frames within movie shots lasting at least
\unit[20]{s} were pseudo-randomly chosen by the following rationale:
% how they were fitted
a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a
movie cut and to another \texttt{no\_cut} event.
% reference to table
A short explanation and counts of these six categories modeled as impulse
events, and six additional event categories for low-level auditory and visual
features of the movie (here again continuous bins lasting \unit[40]{ms}) can be
found in Table \ref{tab:av-events}.
% modeling of regressors from events
Events of both stimuli were convolved with a double gamma hemodynamic response
function (HRF).

@@

% AV COPEs: intro
In context of the AV stimulus, we categorized the frames following a movie cut
irrespective of their concrete visual content and thus without controlling
confounding variables (e.g. presence of faces). The rationale that this
procedure would still be able to isolate the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was simply that activity in the PPA is greater
when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% hence, the following contrasts
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}) by using regressors based on regressors of the AO
stimulus.

>>>>

% AO annotation
For the analysis of the AO stumulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% reference to table with rules and examples
A complete overview of all 18 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in
a] disco'', ``[the platoon wades through a] rice field''). They also comprise
words that could count as a member of another categories in case the narrator
uses these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').

@@

\todo[inline]{SE: Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
    ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum
    GLM unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter;
    COH: I dropped the table of counts per segment.  The information is
    redundant since the counts are not the count of events of the actual
regressors (cf. Table \ref{tab:av-events})}

@@

\paragraph{audio-description: regressors}

% pooling of categories
To create the regressor for the GLM of the AO stimulus, some of
the original 18 categories that were similar but offered only a small amount of
counts were pooled resulting in eleven new categories [that served as
experimental conditionso] (see Table \ref{tab:ao-events}).
% handling of se_new and se_old
Moreover, events that fell into one of the two setting-related categories
(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
treated as belonging to the setting-related category (e.g. ``[a] physician'').
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.

\todo[inline]{Gab es ein separates null-event für jeden zeitraum zwischen zwei
annotierten events oder war das ein regressor der immer wieder kam? COH: uhm,
sorry, what? the following explanation must be misleading?}
% null regressors
If a stimulus segment did not contain an event of a category, a null regressor
was chosen for that category in that segment.\todo{wenn ich "null regressor"
    nehme, darf ich den ganzen Run, glaube ich, in der 2nd level Analyse gar
    nicht benutzen?  Hatte, glaube ich, Jeanette Mumford in einem ihren Videos
mal gesagt}

\todo[inline]{SE: das mit den "five additional categories" habe ich nicht
verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
durchdrungen, und ich glaube damit werde ich nicht alleine sein. COH: }
% categories taken from movie cut annotation
To create contrasts of cross-modal negative control and to capture variance of a
possibly confounding change of the soundscape after a cut, we also implemented
the five movie cut-related regressors used in the GLM of the AV stimulus (see
details below) in the model of the AO stimulus.
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms" ?!?; COH: goddamnit! I've rewritten
    this explanation a lot and finally stuck to the phrasing written in
    \citep{wilson2008beyond} who did the same}
%
Lastly, we created two nuisance regressors based on left-right difference in
volume and root mean square energy averaged across the length of every movie
frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
processes.
% Reference to table
An overview and the respective counts of the eleven speech-related event
categories, the five movie cut-related categories, and the two low-level
confounds can be found in Table \ref{tab:ao-events}.

@@

@@

% AV events
For the analysis of the AV stimulus, we used a previously published annotation
[of the 869] movie cuts and depicted locations \citep{haeusler2016cutanno} to
created regressors based on the kind of location that is depicted in the movie
frame after each cut.

@@

% todo
\todo[inline]{besser erklären (was heißt "unfamilar perspective"? Ab wann ist
ein setting "familiar"?; COH: should be clearer now; maybe rephrase into a
couple of sentences to improve readability}
% AV regressors/events
Each location was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

% to do
\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
zwischen zwei Gesichtern sein?!?; COH: that should be clearer now as the
explanation of the regressors immediately follows the description of the
annotation}
% irrespectible of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables (e.g. presence of
faces).

%%%%%% do not speak of isolate %%%%%%
% AV COPEs: intro
The rationale that this procedure would still be able to isolate the PPA was
twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was simply that activity in the PPA is greater
when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal, grill2006repetition}.

% null regressor
Here again, a null regressor was chosen for segment if it did not contain an
event of specific category.
% no cut condition: intro
A sixth regressors (\texttt{no\_cut}) serving a control condition and to create
negative control contrasts. Frames within movie shots lasting at least
\unit[20]{s} were pseudo-randomly chosen by the following rationale:
% how they were fitted
a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a
movie cut and to another \texttt{no\_cut} event.
% reference to table
A short explanation and counts of these six categories modeled as impulse
events, and six additional event categories for low-level auditory and visual
features of the movie (here again continuous bins lasting \unit[40]{ms}) can be
found in Table \ref{tab:av-events}.
% modeling of regressors from events
Events of both stimuli were convolved with a double gamma hemodynamic response
function (HRF).

@@

% following contrasts
We created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}) by using regressors based on regressors of the AO
stimulus.
